---
title: "Course project"
author: "K. Berezhinskiy"
date: "27/03/2016."
output: html_document
---

Hello! Let's load some libraries!

```{r results='hide',warning=FALSE, message=FALSE}
library(caret)
library (dplyr)
library(ggplot2)
```

Now set up working directory, and load source files.

```{r}
setwd("C:/r/ML")
Train = read.csv("pml-training.csv")
Test<-read.csv("pml-testing.csv")
```

Let's look what is it

```{r}
data.frame(Test=names(Test),Train=names(Train))
```

and visualize

```{r}
qplot(Train$total_accel_belt,Train$classe)
```

Let's drop useless for prediction information, classe variable I will return later

```{r}
Train2<-Train[,-c(1:7,160)]
Test2<-Test[,-c(1:7,160)]
```

Transform classes to numeric, cause it is rather strange to see obviously numeric variables in classes form

```{r, echo=FALSE}
for (i in names(Train2)){
  if (is.numeric(Train2[,i])==TRUE) {next}
  else{
  Train2[,i]<-as.numeric(Train2[,i])}
}

for (i in names(Test2)){
  if (is.numeric(Test2[,i])==TRUE) {next}
  else{
    Test2[,i]<-as.numeric(Test2[,i])}
}
```

Looking for NA in test df (it's important for further prediction)

```{r}
x<-0
i<-1
for (i in c(1:152))
{
  if(is.na(Test2[1,i])==TRUE) {x[i]<-i;}
}
x<-x[!is.na(x)]
x<-x[-1]
x
```

clear Test&Train form useless for prediction NA variables

```{r}
Test3<-Test2[,-x]
Train3<-Train2[,-x]
```
I returned classe as I promised and divided selection for model estimating

```{r}
Train3<-mutate(Train3,classe=Train$classe)
```
```{r}
inTrain <- createDataPartition(y=Train3$classe, p=0.75, list=FALSE)
training <- Train3[inTrain,]
testing <- Train3[-inTrain,]
```


let's create train control function with default options (bootstrapping, p=0.75)

```{r}
tc<-trainControl()
```

Ctrl-enter and go to drink tea with cookies for 1 hour :)

```{r}
modFit1<-train(classe~.,method="rf",data=training,trControl=tc)

```
```{r}
modFit2<-train(classe~.,method="gbm",data=training,trControl=tc)
```


**Accuracy RF**
```{r}
prd1<-predict(modFit1,testing)
confusionMatrix(prd1,testing$classe)
```
**Accuracy boosting**
```{r}
prd2<-predict(modFit2,testing)
confusionMatrix(prd2,testing$classe)

```

We can get conclusion that rm model has better accuracy on current data set. Use it and get final result

```{r}
predict(modFit1,Test3)

```


Thank you for attention!

